---
title: "ModelingWithCopula"
author: "Duc-Anh Nguyen"
date: "2025-02-03"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## First case study:
Goal: to analyse the rainfall in Germany in summer
For that we model the bivariate distribution of summed precipitation over a whole summer in kg/m^2 at 2 measuring stations pr1,pr2. 

Therefore , we describe a bivariate distribution function F<sub>12</sub>(x<sub>pr1</sub>, x<sub>pr2</sub>) by a gumbel copula C<sub>12</sub> with parameter θ = 5. In the case of both stations, the marginal distribution of precipitation is modeled by a Pareto distribution
```{r}
library(ggplot2)
# Load the dataset
rain <- read.csv("precipitation_germany.csv")
rain |> head()
rain |> dim()
```
We will now try to estimate F<sub>12</sub> using a Gumbel copula. We will carry these steps:
 • Transform the dataset using the empirical cumulative density function.
 • Fit a copula model to the transformed data, a one-parametric one
 • Identify the most suitable copula family using the AIC criterion.

```{r}

# Load necessary libraries
#install.packages("VineCopula")
library(VineCopula)
# install.packages("rvinecopulib")
library(rvinecopulib) 
# Transform data to pseudo-observations
u_rainfall <- pseudo_obs(rain)
u_rainfall

# Fit copula model and select the best family by AIC

copula_rainfall = bicop(data = u_rainfall, family_set = "onepar", selcrit = "aic")

# Summarize the fitted copula
summary(copula_rainfall)
```
Interpretation: 
+ pseudo_obs estimates the empirical cumulative density (ECD) to transform the data on the 2D Uniform Hyper-cube 

+ bicop() estimates the parameters of all single parametric copula families and pics the most suitable family by AIC

+ the output describes a bivariate Joe copula with a 90-degree rotation, fitted to a dataset of 1000 continuous observations. The 90-degree rotation implies that the copula is modeling lower tail dependence rather than the upper tail dependence typically associated with the Joe copula.

+ criterion summary shows that the most suitable copula is a non-rotated gumbel copula where θ = 1.03,  suggesting weak dependence between the two variables.



## Second case study:

```{r}

library(dplyr)
load("muc.Rdata")
head(muc3)
skimr::skim(muc3)

# restrict to stunde = 20, to a few specific numeric covariates and remove NAs
muc20 <- muc3 %>%
  filter(stunde == 20) %>%
  select(PM10_luis, PM10_Loth, PM10_Prin, PM10_Stach, NO_Loth, NO2_Loth) %>%
  na.omit()

skimr::skim(muc20)


# visualising data with scatter plot matrix
pairs(muc20, pch = ".", gap = 0)

```


```{r}


```


```{r}


```


```{r}


```


```{r}


```
